%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
% \addbibresource{bibliography.bib}

\begin{document}
\header{David}{Dias}
       {Enthusiastic Engineer}

% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    Lisbon, Portugal
    ~
    \href{mailto:mail@daviddias.me}{mail@daviddias.me}
    \href{http://daviddias.me}{http://daviddias.me}
    \href{https://twitter.com/daviddias}{t://daviddias}
    \href{https://github.com/diasdavid}{g://diasdavid}
  \section{languages}
    Portuguese
    English
  \section{skills}
    {\color{red} $\varheartsuit$} JavaScript
    (ES5, node.js)
    Python, C, C\#, Java
    CSS3 \& HTML5
    TCP/IP networks
    Notions of Photoshop \& Illustrator
\end{aside}

\section{interests}

cloud computing, peer to peer networks, information security, information retrieval, communication networks and entrepreneurship

\section{education}

\begin{entrylist}
  \entry
    {2012}
    {M.Sc. in Communication Networks Engineering}
    {Technical University of Lisbon, Portugal}
    {Majoring in Cloud Computing, P2P Networks and Mobile Applications. \\
        - Developed the world's first DHT for the Browser based on the Chord P2P Algorithm and using WebRTC as the layer of transport - https://github.com/diasdavid/webrtc-explorer}
  \entry
    {2008 - 2012}
    {B.Sc in Communication Networks Engineering}
    {Technical University of Lisbon, Portugal}
    {Specializing in computer science, TCP/IP networks, distributed systems and information security.}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {2014 \& 2015}
    {\&yet - Lisbon -  WA, USA}
    {Node.js Developer, Junior Pentester, Business Development Lead.}
    {\emph{Some achievements:\\
        - Development the `nsp`vulnerable dependency checker and respective ecosystem of modules - https://www.npmjs.com/package/nsp\\
        - Tripled the amount of revenue generated by the Lift Security team by restructuring and optimizing the business development process.\\
        - Sucessfully develop and deliver the first Node.js Security Training, helping several teams deliver better code.}}
  \entry
    {2013 \& 2014}
    {The Node Firm, Lisbon - San Francisco}
    {Node.js Engineer}
    {\emph{Backend developer, focused on Node.js development. Letter of recomendation: \href{http://thenodefirm.com/blog/2014/01/31/david-dias-joins-node-security/index.html}{http://thenodefirm.com/blog/2014/01/31/david-dias-joins-node-security/index.html }}}
  \entry
    {2013}
    {The Node Firm, Lisbon - San Francisco}
    {Summer Internship.}
    {\emph{Backend developerl.}}
  \entry
    {2012 - 2014}
    {LXJS - Lisbon Javascript Conference}
    {Curator.}
    {\emph{2 day conference, for the community, by the community and not for profit about the new worlds of Javascript.\\
    What people said so far: \\
      - Jan Lehnardt (JSConfEU Lead): “LxJS was a riot. A must-attend conference. Much <3 to the team for put this together”\\
      - James Chesters (10gen Community Lead): “LxJS is easily one of the best conferences I’ve been to, ever. Being community  organised and not-for-profit makes it all the better”.}}
  \entry
    {2013}
    {\href{http://startupscholarship.org/}{The Startup Scholarship, Lisbon}}
    {Co-Founder and COO.}
    {\emph{The Y combinator of startup internship, summer school and community immersion program for international students to experience in Lisbon.}}
  \entry
    {2013}
    {IEEE Computer Society, EMEA}
    {Membership Development Coordinator for R8(EMEA).}
    {\emph{Created the \'CS Trainings Program\', a student trainers network to propagate extra expertises amongst EMEA universities.}}    
\end{entrylist}
\begin{entrylist} 
  \entry
    {2012-2013}
    {Google Student Ambassador, Europe}
    {Student Representative.}
    {\emph{Organized the first Google DevFest in Portugal, one of the biggest DevFest in the World, 220 Developers, 24 hour hackathon, 16 technical hands on sessions from professionals of Web Development and Mobile Development.\\
    - Won the GSA Google+ Competition.}}
  % \entry
  %   {2013}
  %   {IEEE R8 Student Activities Committee, EMEA}
  %   {Electronic Activities Coordinator.}
  %   {\emph{SOMETHING SOMETHING.}}
  \entry
    {2011-2012}
    {IEEE-IST Student Branch, Lisbon}
    {Chairperson.}
    {\emph{Achievements:  \\
      33\% Increase in active members (first time over 10\%).\\
      750\% increase in activities (from 4 a year to 30 a year).\\
      Most successful Teacher-In-Service Program in the world.}}      
  \entry
     {2012}
     {Run \& Slide Summer Camp, Portugal}
     {Summer Job - Teenager Entretainer and Coordinator.}
     {\emph{Coordinated a team of 10 young individuals in 15 days non-stop outdoor activities.}}
  \entry
    {2012}
    {IST, UTL Computer Science Department, Lisbon}
    {Research Scholarship.}
    {\emph{Developed productivity training based on software tools for high school teachers and college freshmen.}}
  \entry
    {2010-2012}
    {IEEE Portugal Section, Portugal}
    {Web master.}
    {\emph{Maintained and migrated all webpages from a Free BSD instance on SUN Spark machine to a newer Intel based server running Ubuntu Server.}}
  % \entry
  %   {07–08 2004}
  %   {IST, UTL Math Department, Lisbon}
  %   {Research Scholarship.}
  %   {\emph{SOMETHING SOMETHING.}}  

\end{entrylist}

\section{awards}

\begin{entrylist}
  \entry
    {2012}
    {Richard E. Merwin Award by IEEE Computer Society}
    {}
    {For demonstrating outstanding involvement in IEEE Computer Society, for Academic Excellence and for Student Leadership.}
  \entry
    {2011}
    {IEEE Webpage Contest}
    { }
    {1st Place of IEEE Region 8 (EMEA) Webpage Contest and 3rd Place IEEE Global Webpage Contest.}
  \entry
    {2011}
    {Microsoft}
    {}
    {1st Place at Windows Phone App Code Camp by Microsoft in 2011.}
  \entry
    {2011}
    {BET - Bring Entrepreneurs Together}
    {}
    {2nd Place with honorable award at Google Case Study Competition in BET24 Entrepreneurs Challenge.}    
\end{entrylist}

% \section{publications}

\end{document}
